---
title: Time required for plink to run on Biobank
date: "`r Sys.Date()`"
output: 
  pdf_document
---

```{r, echo=FALSE}
suppressPackageStartupMessages(suppressWarnings(library(knitr)))
opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE)
```

```{r }
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(lubridate))

# Read in times and lengths
a <- read.table("times.txt", sep=",", stringsAsFactors=FALSE)
a$time <- ymd_hms(as.POSIXct(strptime(a$V3, "%a %b %e %T %Y")))

b <- group_by(a, V1) %>% dplyr::summarise(hrs = (time[1] %--% time[2]) / dhours(1)) %>% as.data.frame()
b$nsnp <- scan("lengths.txt", numeric())
names(b)[1] <- "chr"

```

Timings for:

- 120000 samples
- 15 covariates
- linear model
- `r formatC(sum(b$nsnp), digits=7)` SNPs
- Single core per chromosome

```{r }
kable(b)
```

```{r }
plot(hrs ~ nsnp, b, ylim=c(0,37), xlim=c(0,8e5), xlab="Number of SNPs", ylab="Time (hours)")
abline(lm(hrs ~ nsnp, b))
```

**Total time for a single core:** `r round(sum(b$hrs),2)` hours.

**Predicted time for 28 cores:** `r round(sum(b$hrs) / 28,2)` hours.

**Note:** Running chr 22 again on its took 3.75 hours, substantially less than when things are run together. This is probably because 16 cores reading in data concurrently led to a much longer read-in time. Reducing the biobank data size in terms of number of SNPs would probably improve things, these analyses were run on the unfiltered data.
